CDSR Human Data/Modelling Paper

### 2013-09-13 scenarios/cdsr/trunk/papers/ACS2013/main.tex

% \author{Pat Langley}{langley@asu.edu}
% \author{Glen Hunt}{glen.hunt@asu.edu}
% \address{Computing Science and Engineering, Arizona State University, 
%          Tempe, AZ 85287 USA}
% \author{Daniel G.\ Shapiro}{dgs@isle.org}
% \address{Institute for the Study of Learning and Expertise, 
%          2164 Staunton Court, Palo Alto, CA 94306 USA}
\vskip 0.2in

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider an agent asked to remain ``in the safe zone'' during a military engagement.  The size, shape, and location of this area depend on the capabilities of the agent, other agents in the scene, and the constraints imposed by the environment.  We call these types of regions \textit{context-dependent spatial regions}(CDSRs) due to the context-dependent nature of their extent.  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment as well as understanding how task-specific information influences spatial interpretation.  We report the results of a human study conducted to explore how people interpret three types of CDSRs and to support the knowledge integration claim.  We discss the implications for these results on cognitive systems development.
\end{abstract}

@@

Section~\ref{sec:cdsrs} discusses the features of CDSRs using illustrative examples.  We claim that (1) people can effectively communicate using these regions, and (2) the size and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new contexts, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

@@

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
  \begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
  \caption{\textit{The front of the classroom} could be defined as the area between the desks and the whiteboard where people give presentations.}
  \end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
  \caption{\textit{Safety for the scout} is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
  \caption{A \textit{bottleneck} occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
  \label{fig:safety}
  \end{subfigure}

  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

Understanding these regions is crucial to joint intelligent action with humans.  Not only are these regions frequently tied to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety'', but they are also central to understanding human activities: e.g., ``Is there a class in session?''.

The long-term goal of our work is to create cognitive systems that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new contexts.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

@@

We developed the study described below in order to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular context how well do people agree on the location and extent of a named CDSR?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given context effect the location and extent of a named CDSR?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining variation in CDSR placement within different situations. In a context exhibiting clear contextual clues (e.g. determining a safe zone in a battle context where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. In a less well-defined context, one might expect little to no agreement between human communicators.  Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

@@

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli such that it defined the extent of the CDSR in the scene (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well it fit with their understanding of the CDSR on a five point likert scale.
\end{itemize}

Both Task 1 and 2 address both research questions. Between subject agreement metrics can be computed for both Task 1 and Task 2. In particular, a variation in between subject agreement across the different contexts for a particular CDSR could be taken as evidence that some contexts are more amenable to a particular CDSR than others and hence CDSRs are contextually dependent. By shifting the focus of the analysis to examining the variation in responses for a given CDSR in context that differed only with respect to the location of objects both the results from both tasks can address research question 2. In the case of Task 1 the variation we will examine is the area of the polygons, while in Task 2 the variation we will examine is the scoring of the marked locations.

We developed a set of visual stimuli depicting different environments, and paired each with an accompanying linguistic description of a CDSR easily understood within the context of that environment (see Figure \ref{fig:exp_stimuli}). These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the domain and the spatial region that accompanied them: (1) the classroom domain stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the military engagement stimuli were always accompanied by the description \emph{safety}; and (3) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}.

@@

\subsection{Participants and Procedure}
Using these stimuli pairs, we developed an online experiment with two different types of trials to explore our initial questions. 43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised for each participant as was the order of the stimuli presented within each trial.

\subsection{Task 1 - Design}
In the first set of trials, the subject was asked to draw a polygon that defined the extent of the CDSR given or to select a no region option.  The drawing was done on the diagram in all stimuli with the classroom photographs provided for reference in those trials.  Subjects drew polygons by clicking to position the vertices with lines being automatically generated between each point indicated as the subject drew.  There was no upper bound placed on the number of line segments drawn but subjects were required to provide at least three line segments or to choose no region before continuing to the next stimulus.

@@

\begin{table}[t]
\parbox{.35\linewidth}{
\begin{tabular}{l c c}
% Stim ID & Average Pairwise $\kappa$ & No Region Responses\\
 & Average & No \\
Stim ID & Pairwise $\kappa$ & Reg.\\
\hline
\hline
(h) & 0.5034 & 0\\ % 1_2
(g) & 0.4585 & 1\\ % 1_1
(k) & 0.4548 & 0\\ % 3_3
(f) & 0.3930 & 0\\ % 2_4
(i) & 0.3906 & 0\\ % 3_1
(e-flipped) & 0.3813 & 2\\ % 2_3
(j) & 0.3787 & 1\\ % 3_2
(f-flipped) & 0.3720 & 2\\ % 2_5
(e) & 0.3629 & 1\\ %2_2
(l) & 0.3164& 0\\ % 3_4
(c) & 0.2438 & 2\\ % 2_6
(c-flipped) & 0.2414 & 4\\ %2_7
(a) & 0.0996 & 10 \\ % 2_1
\hline
\end{tabular}
\label{tab:stimuli-kappa-scores}
\caption{The average pairwise $\kappa$ scores and the number of no region response by visual stimuli.}
}
\hfill
\parbox{.65\linewidth}{
\begin{tabular}{c c}
Expected Relationship & Human Results  \\
\hline
\hline
area(g) > area(h) & 291.2 > 276.2 (p<.003) \\
maximumX(f) > maximumX(e) & 176.1 > 167.1   (p<.47) \\
% minimumX(e-flipped) > minimumX(f-flipped) & 336.1 > 321.3 (p<.12) \\
minimumX(e-flipped)  &  \\
 > minimumX(f-flipped) & 336.1 > 321.3 (p<.12) \\
maximumY(i) > maxmimumY(j) & 304.64 > 265.04 (p<.03) \\
maximumY(j) > maxmimumY(k) & 265.04 > 251.71 (p<.47) \\
maximumY(k) = maxmimumY(l) & 265.04 != 290.03 (p<.04) \\
\hline
\end{tabular}
\label{tab:region-location-tests}
\caption{Comparison of the expected relationships to the mean human responses.}
}
\end{table}

@@

Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no region responses for each stimuli.  It is clear from this table that the less common stimuli have the lowest $\kappa$ scores.  Each of the non-typical regions, the turret +1 arrangement (l), the u-shaped layouts (c and c-flpped), and the circle layout score have kappa scores of less than 0.35. Looking at the classroom results as a whole, these results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment.  This dependence is observed by the fact that just moving the desks into a circle configuration the CDSR for the front of the room no longer exists.

@@

\subsection{Task 2 - Design} 
In the second set of trials, a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region.  The location of these points was informed by the results of a pilot study. In the final study they were positioned such that one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli (as shown in Figure \ref{fig:classroom-points}). One of the aims of this configuration of points was to provide comparable data points between the trials where the classroom stimuli were horizontally flipped. In the classroom domain the expected sweetspot varied between the points depending on the stimuli. In the map domain P1 was positioned in the top left corner of the stimuli,  P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the top of the image in the proximity of the enemy tanks, P2 was located near the center of the image such that in some stimuli it was in a no-man's land position and in other stimuli (specifically stimuli (i) in the friendly tanks have moved forward and (l) where there is an extra friendly turret) it could be considered to be in a protected area, and P3 was located near the bottom of the stimuli and consequently was always located behind the friendly tanks/turrets. P3 was the expected sweetspot in the military engagement domain but it was also hoped that P2 rating would differ between the stimuli where it was in no-mans land and where it recieved some protection.

@@

Table \ref{tab:point-likert-scores} lists the average likert scores for the different points in each domain. For each stimuli we have highlighted in bold the maximum average likert rating for a point for that stimuli. In all cases the expected sweetspot received the maximum average likert rating for trials using that stimuli. For each stimuli we tested whether the higher ratings of the sweetspot locations was statistically significant using one-tailed two sample t-tests and in all cases the ranking of the sweetspot was found to be significantly higher than either of the other two points using a confidence level of $95\%$. 
%There were two of these t-tests carried out for each stimuli, each one tested whether the sweetspot ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimuli. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the sweetspot was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. %lending support for question 2 ...

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c c c c c }
\hline
\hline
%Domain & \multicolumn{7}{l}{Map/Bottleneck} \\
\textbf{Map} & g & h & ~ & ~ & ~ & ~ & ~ \\ 
P1 & $1.1707$ & $1.1707$ & ~ & ~ & ~ & ~ & ~ \\
P2 & $\mathbf{4.6667}$ & $\mathbf{4.7561}$ & ~ & ~ & ~ & ~ & ~ \\
P3 & $1.85$ & $1.585$ & ~ & ~ & ~ & ~ & ~ \\
\hline
%Domain & \multicolumn{7}{l}{Classrom/Front of Room} \\
\textbf{Classroom}& a & c & c-flipped & e & e-flipped & f & f-flipped \\
P1 & $\mathbf{3.5122}$ & $\mathbf{4.7073}$ & $1.244$  & $\mathbf{4.7561}$ & $1.2439$ & $\mathbf{4.8292}$ & $1.1463$\\
P2 & $2.6341$ & $2.9024$ & $2.9268$ & $2.0000$ & $1.8500$ & $2.0976$ & $2.3171$\\
P3 & $1.9024$ & $1.3571$ & $\mathbf{4.6429}$ & $1.2439$ & $\mathbf{4.7073}$ & $1.2750$ & $\mathbf{4.6585}$\\
\hline
%Domain & \multicolumn{7}{l}{Military Engagement/Safe Region} \\
\textbf{Military} & i & j & k & l & ~ & ~ & ~ \\
P1 & $1.1951$ & $1.0952$ & $1.0714$ & $1.2327$ & ~ & ~ & ~ \\
P2 & $4.3902$ & $2.2927$ & $2.7804$ & $3.1667$& ~ & ~ & ~ \\
P3 & $\mathbf{4.9024}$ & $\mathbf{4.5122}$ & $\mathbf{4.6585}$ & $\mathbf{4.7073}$ & ~ & ~ & ~ \\
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain and stimulus.}
\end{table}

@@

Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.

However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.

The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

>>>>

\author{Kate Lockwood}{klockwood@csumb.edu}
\address{ITCD Department, California State University - Monterey Bay}
\author{John D. Kelleher}{john.d.kelleher@dit.ie}
\address{Applied Intelligence Research Centre, Dublin Institute of Technology }
\author{Matthew Klenk}{klenk@parc.com}
\address{Palo Alto Research Center, Palo Alto CA }
\author{Nick Hawes}{n.a.hawes@cs.bham.ac.uk}
\address{Intelligent Robotics Lab, University of Birmingham, UK }
\vskip 0.2in

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider an agent asked to remain ``in the safe zone'' during a military engagement.  The size, shape, and location of this area depend on the capabilities of the agent, other agents in the scene, and the constraints imposed by the environment.  We call these types of regions \textit{context-dependent spatial regions} (CDSRs) due to the context-dependent nature of their extent.  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment as well as understanding how task-specific information influences spatial interpretation.  We report the results of a human study conducted to explore how people interpret three types of CDSRs and to support the knowledge integration claim.  We discss the implications for these results on cognitive systems development.
\end{abstract}

@@

We claim that (1) people can effectively communicate using these regions, and (2) the size, location and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new contexts, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

@@

%Combine these figures into a single figure across
\begin{figure}
\centering
%% Change the classroom to be a picture stimuli
\begin{tabular}{c c c} 
  \begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/classroom.png}
%  \caption{\textit{The front of the classroom} could be defined as the area between the desks and the whiteboard where people give presentations.}
  \caption{\textit{The front of the classroom}.}
  \end{subfigure} &
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/safety-3.jpg}
%  \caption{\textit{Safety for the scout} is contextually defined by the location of the friendly turrets and the capabilities of the opposing force.}
  \caption{\textit{The safe region for the scout}.}
\end{subfigure} & 
\begin{subfigure}[b]{0.32\textwidth}
  \includegraphics[width=\textwidth]{figures/bottleneck.JPG}
%  \caption{A \textit{bottleneck} occurs when paths are confined to a narrow region by geographic features.  In this case, the water prevents ground movement.}
 \caption{\textit{The bottleneck}.}
  \label{fig:safety}
  \end{subfigure}\\
\end{tabular}
  \caption{Examples of spatial regions used as stimuli in our experiments.}
  \label{fig:examples}
\end{figure}

Understanding these regions is crucial to joint intelligent action with humans; among other reasons they are frequently tieds to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety''. In the rest of the paper we present a study that examined the contextual dependence of these regions and dicuss the implications that these t. Following this we discuss the implications of these regions for the development of cognitive systems.

%JK Removed the following text and replaced with text above primarily to save space, feel free to switch back.
%  Not only are these regions frequently tied to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety'', but they are also central to understanding human activities: e.g., ``Is there a class in session?''.
%The long-term goal of our work is to create cognitive systems that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new contexts.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

@@

We developed the study described below in order to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular context, do people agree on the location and extent of a named CDSR?
	\item Does changing the context in a given scenario predictably effect the CDSR?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining: (a) whether or not a CDSR is always applicable in a given enviroment (more bluntly, does a classroom always have a front or is this dependent on the configuration of objects in the room), and (b) the variation in CDSR placement and size within different context. Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

%In a context exhibiting clear contextual clues (e.g. determining a safe zone in a battle context where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. However, in the same environment (classroom, geographic location) but with less well-defined context, one might expect little to no agreement between human communicators.

@@

We developed two experimental tasks that each address both research questions:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli that defined the CDSR (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well the location fitted with their understanding of the CDSR on a five point likert scale.
\end{itemize}

We developed a set of visual stimuli depicting different contexts, and paired each with an accompanying linguistic description of a CDSR (see Figure \ref{fig:exp_stimuli}). These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the situation: (1) the classroom stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the military engagement stimuli were always accompanied by the description \emph{safety}; and (3) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}.

@@

%\subsection{Participants and Procedure}
%Using these stimuli pairs, we developed an online experiment with two different types of trials to explore our initial questions. 43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised for each participant as was the order of the stimuli presented within each trial.

\textbf{Participants and Procedure:} The experiment was delivered online. 43 undergraduate students from two third level institutes took part in the study. To control for sequence effects the order of the trials were randomised for each participant as was the order of the stimuli within each trial.

\subsection{Task 1 - Design}
In task one, the subject was asked to draw a polygon that defined the extent of the CDSR given or to select a no region option.  The drawing was done on the diagram in all stimuli with the classroom photographs provided for reference in those situations.  Subjects drew polygons by creating a sequence of vertices with lines being automatically generated between them as the subject drew.  There was no upper bound placed on the number of line segments drawn but subjects were required to provide at least three line segments or to choose no region before continuing.

@@

\begin{table}[t]
\parbox{.50\linewidth}{
\centering 
\begin{tabular}{l c c}
% Stim ID & Average Pairwise $\kappa$ & No Region Responses\\
 & Average & No \\
Stim ID & Pairwise $\kappa$ & Reg.\\
\hline
\hline
(h) & 0.5034 & 0\\ % 1_2
(g) & 0.4585 & 1\\ % 1_1
(k) & 0.4548 & 0\\ % 3_3
(f) & 0.3930 & 0\\ % 2_4
(i) & 0.3906 & 0\\ % 3_1
(e-flipped) & 0.3813 & 2\\ % 2_3
(j) & 0.3787 & 1\\ % 3_2
(f-flipped) & 0.3720 & 2\\ % 2_5
(e) & 0.3629 & 1\\ %2_2
(l) & 0.3164& 0\\ % 3_4
(c) & 0.2438 & 2\\ % 2_6
(c-flipped) & 0.2414 & 4\\ %2_7
(a) & 0.0996 & 10 \\ % 2_1
\hline
\end{tabular}
\caption{The average pairwise $\kappa$ scores and the number of no region response by visual stimuli.}
\label{tab:stimuli-kappa-scores}
}
\hfill
\parbox{.50\linewidth}{
\centering
\begin{tabular}{c c}
Expected Relationship & Human Results  \\
\hline
\hline
area(g) > area(h) & 291.2 > 276.2* \\
maxX(f) > maxX(e) & 176.1 > 167.1 \\
% minimumX(e-flipped) > minimumX(f-flipped) & 336.1 > 321.3 (p<.12) \\
minX(e-flipped)  &  \\
 > minX(f-flipped) & 336.1 > 321.3* \\
maxY(i) > maxY(j) & 304.64 > 265.04* \\
maxY(j) > maxY(k) & 265.04 > 251.71 \\
maxY(k) = maxY(l) & 265.04 != 290.03 \\
\hline
\end{tabular}
\caption{Comparison of the expected relationships to the mean human responses.}
\label{tab:region-location-tests}
}
\end{table}

@@

Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no region responses for each stimuli.  It is clear from this table that the less common stimuli have the lowest $\kappa$ scores.  Each of the non-typical regions, the turret +1 arrangement (l), the u-shaped layouts (c and c-flpped), and the circle layout score have kappa scores of less than 0.35. Looking at the classroom results as a whole, these results support the hypothesis that the definition of CDSRs in a given context is effected by the location and orientation of objects in the environment.  This dependence is observed by the fact that just moving the desks into a circle configuration the CDSR for the front of the room no longer exists.

@@

Table \ref{tab:region-location-tests} compares the expected relationships between the geometric extent of the same region type between different contexts.  In five of the six comparisons, the expected relationships were found in human data supporting our claim that changes of context systematically change the extents of the regions.  The comparison of the safety area with tanks (j) versus turrets (k) is interesting because it provides some evidence that people are simulating actions of other agents in the scene.  That is, because the tanks can move and turrets cannot, the safe region extends higher on screen in the tanks context.  The case that did not demonstrate the expected the relationship was the safety region between the row of turrets (k) and turrets +1(l).  Our expectation was that people would reason that a lone turret would be no match for three tanks and indicate the safe region.  A possible explanation for this is that there is a domain expertise component to understanding contexts.

\subsection{Task 2 - Design} 
In task two, a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region, or select not applicable.  The location of these points was informed by the results of a pilot study, such that one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain, the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli. This provides comparable data points between the trials where the classroom stimuli were horizontally flipped.  In the geography situations, P1 was positioned in the top left corner of the stimuli, P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the enemy tanks, P3 was located with all friendly units between the it and the enemy tanks and P2 was located near the center of the image as follows. In stimuli (j,k) the point lay between all forces, in stimuli (i), it lay behind the friendly tanks, and in stimuli (l) , it behind the lone turret but in front of the row turrets.  P3 was the expected sweetspot in the military engagement domain but the rating of P2 should differ with context receiving the highest score in (i) and the lowest score in (k).

@@

Table \ref{tab:point-likert-scores} lists the average likert scores for the different points in each context. In all context, the expected sweetspot received the maximum average likert rating that was statistically significant using one-tailed two sample t-tests $(p<.05)$.  To control for left-right bias, we compared the ratings of sweetspots in the classroom stimuli (c,e and f) with their flipped variants.  There was no statistical difference between the stimuli and their flipped variants.  These likert ratings on individual stimuli supports the claim that people are able to agree on the locations of CDSRs with changing context.

%There were two of these t-tests carried out for each stimuli, each one tested whether the sweetspot ranking was statistically higher than one of the other points. Table \ref{tab:point-likert-scores} also lists the results of these t-tests for each stimuli. In all cases, the results indicate that the null hypothesis, $H_0$, should be rejected and that the alternative hypothesis, namely that the sweetspot was rated significantly higher than the other point, could be accepted with $\alpha=0.05$.

%As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. %lending support for question 2 ...

% The following paragraph should end by saying this about question 1.

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c c c c c }
\hline
\hline
%Domain & \multicolumn{7}{l}{Map/Bottleneck} \\
\textbf{Map} & g & h & ~ & ~ & ~ & ~ & ~ \\ 
P1 & $1.1707$ & $1.1707$ & ~ & ~ & ~ & ~ & ~ \\
P2 & $\mathbf{4.6667}$ & $\mathbf{4.7561}$ & ~ & ~ & ~ & ~ & ~ \\
P3 & $1.85$ & $1.585$ & ~ & ~ & ~ & ~ & ~ \\
\hline
%Domain & \multicolumn{7}{l}{Classrom/Front of Room} \\
\textbf{Classroom}& a & c & c-flipped & e & e-flipped & f & f-flipped \\
P1 & $\mathbf{3.5122}$ & $\mathbf{4.7073}$ & $1.244$  & $\mathbf{4.7561}$ & $1.2439$ & $\mathbf{4.8292}$ & $1.1463$\\
P2 & $2.6341$ & $2.9024$ & $2.9268$ & $2.0000$ & $1.8500$ & $2.0976$ & $2.3171$\\
P3 & $1.9024$ & $1.3571$ & $\mathbf{4.6429}$ & $1.2439$ & $\mathbf{4.7073}$ & $1.2750$ & $\mathbf{4.6585}$\\
\hline
%Domain & \multicolumn{7}{l}{Military Engagement/Safe Region} \\
\textbf{Military} & i & j & k & l & ~ & ~ & ~ \\
P1 & $1.1951$ & $1.0952$ & $1.0714$ & $1.2327$ & ~ & ~ & ~ \\
P2 & $4.3902$ & $2.2927$ & $2.7804$ & $3.1667$& ~ & ~ & ~ \\
P3 & $\mathbf{4.9024}$ & $\mathbf{4.5122}$ & $\mathbf{4.6585}$ & $\mathbf{4.7073}$ & ~ & ~ & ~ \\
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Sitaution and Stimulus.}
\end{table}

@@

%Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.
%
%However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.
%
%The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

%JK Previous version above I replaced it with this shorter version below
